### 2024-03-29 doc/sections/mav-syntax.tex
Part of pushing through syntactic stuff

The structures of MAV are formed from positive and negative atoms ($\vPos\va$ and $\vNeg\va$), units ($\vUnit$), the non-commutative connective \emph{seq} ($\vSeq$), the multiplicative connectives \emph{tensor} and \emph{par} ($\vTens$ and $\vParr$) and additive connectives \emph{with} and \emph{plus} ($\vWith$ and $\vPlus$).

@@

Note that, except for \cref{rule:Switch}, the rules come in pairs that are dual, in the sense that if a rule is of the form $P \vInferFrom Q$, then its partner is of the form $\vDual{P} \vInferFrom \vDual{Q}$. The \cref{rule:Switch} rule is, up to commutativity, already its own dual. The \cref{rule:Cut}, \cref{rule:CoLeft}, and \cref{rule:CoRight} rules introduce of new formulas going left-to-right. Normal proofs, which we define below, avoid these \emph{synthetic} rules.

\begin{definition}
  \emph{Derivation}, written $\vInferFrom*$ is the reflexive,
  transitive closure of inference.  \emph{Invertible inference},
  written $\vBiInfer$, is the symmetric core of $\vInferFrom$, \ie
  ${\vBiInfer} = {\vInferFrom\cap\vInferTo}$.  \emph{Invertible
    derivation}, written $\vBiInfer*$, is the symmetric core of
  derivation, or, alternatively, the reflexive, transitive closure of
  invertible inference.  \emph{Proofs} are derivations that terminate
  in the unit, \eg a derivation $\vP\vInferFrom*\vUnit$ is a proof of
  $\vP$.
\end{definition}

>>>>

The structures of MAV are formed from positive and negative atoms ($\vPos\va$ and $\vNeg\va$) drawn from some set of atomic propositions, units ($\vUnit$), the non-commutative connective \emph{seq} ($\vSeq$), the multiplicative connectives \emph{tensor} and \emph{par} ($\vTens$ and $\vParr$) and additive connectives \emph{with} and \emph{plus} ($\vWith$ and $\vPlus$).

@@

Note that, except for \cref{rule:Switch}, the rules come in pairs that are dual, in the sense that if a rule is of the form $\vP\vInferFrom\vQ$, then its partner is of the form $\vDual\vP\vInferFrom\vDual\vQ$. The \cref{rule:Switch} rule is, up to commutativity, already its own dual. The \cref{rule:Cut}, \cref{rule:CoLeft}, and \cref{rule:CoRight} rules introduce of new formulas going left-to-right. Normal proofs, which we define below, avoid these \emph{synthetic} rules.

\begin{definition}\label[defn]{defn:derivation}
  \emph{Derivation}, written $\vInferFrom*$ is the reflexive, transitive closure of inference.  \emph{Invertible inference}, written $\vBiInfer$, is the symmetric core of $\vInferFrom$, \ie ${\vBiInfer} = {\vInferFrom\cap\vInferTo}$. \emph{Invertible derivation}, written $\vBiInfer*$, is the symmetric core of derivation.  \emph{Proofs} are derivations that terminate in the unit, \eg a derivation $\vP\vInferFrom*\vUnit$ is a proof of $\vP$.
\end{definition}
